Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-29 Manuscript.Rmd
had to fix an incorrect p = 0

---
title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference_draft.docx
  pdf_document: 
    keep_tex: true
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`). These results suggest that some nodes were considerably variable in time, despite overall stability in the community arrangement.**

>>>>

---
title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: 
    keep_tex: true
  word_document: 
    reference_docx: Style_reference_draft.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`). These results suggest that some nodes were considerably variable in time, despite overall stability in the community arrangement.**
